---
title: "Priors_for_Learning_Outcome_Model"
author: "SM"
date: "2023-10-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

Forming Priors

Prior distributions for our model are set based on previous literature and inputs from experts. Experts' inputs are obtained via focused group discussion and survey. 

## Stage 1: Priors from literature

The objectives of collecting prior information from literature:

- To identify variables that have direct association with the targeted outcome
- To identify the direction and degree of associations between the variables and the outcome
- To explore the changes in values of outcomes affected by different variables (when         applicable)

### Applicability and generalizability of data on our population 

The applicability and generalizability of data are determined by the extent of similarity between the study population and our population. 

#### Background info of our population

+ Location- Yangon, Myanmar
+ Population- Professional football players
+ Gender- Male and Female 
+ Age- 15 to 30
+ Education level- highschool to college level students, older players are university           graduates

#### Intervention 1: Improving Nutritional Self-reliance

+ Nutrition education (Nutrition Guide and a series of in-person classes)
    + Food groups (basic level)
    + Types of nutrients (basic level)
    + Healthy plate (basic level)
    + Macronutrient and fluid requirements (Intermediate to advance level)
    + Calculation of protein-energy requirements (Advance level)
    + Food exchange (Advance level)

#### Intervention 2: Guided Personalized Nutrition

+ Nutrition education (a 3-hour in-person class)
    + Food groups (basic level)
    + Types of nutrients (basic level)
    + Healthy plate (basic level)
    + Macronutrient and fluid requirements (Intermediate level)
    
### Collecting Priors from Literature Review

> 1. [The influences of interest in learning and learning hours on learning outcomes
of vocational college students in Taiwan: using a teacher’s instructional attitude
as the moderator](http://wiete.com.au/journals/GJEE/Publish/vol13no3/01-Lee-Y-J.pdf)


```{r table1, tidy=FALSE, include=FALSE} 

data1 <- tribble(
  ~"Name",                  ~"Category",                          ~"Match",
  "Location",                "Taiwan",                              "Low",
  "Population",              "College students, lecturers",         "Medium",
  "Gender",                  "Male and Female",                     "High",
  "Age",                     "18 to 60",                            "Medium",
  "Education level",         "College studnets to Phd",             "Medium",
  "**Applicability**",       "**NA**",                              "**Low to Medium**"
)
knitr::kable((data1), booktabs = TRUE,
caption = 'Study Population')

```

```{r table2, tidy=FALSE, include=FALSE}
data2 <- read.table(stringsAsFactors = FALSE, header = TRUE, sep="/", text =
'Name/Category/Match
 Location/Taiwan/Low
 Population/College students, Lecturers/Medium
 Age/ 18 to 60/ Medium
 Education level/ College students to Phd/ Medium
 Applicability/ NA/ Low to Medium'
)
knitr::kable((data2), booktabs = TRUE,
caption = 'Study Population')
```

<style>
.column-left{
  float: left;
  width: 33%;
  text-align: left;
}
.column-center{
  display: inline-block;
  width: 33%;
  text-align: center;
}
.column-right{
  float: right;
  width: 33%;
  text-align: right;
}
</style>

#### $\color{brown}{\text{Study Population}}$

<div class="column-left">
**Category**

Location

Population

Age

Education level

*Applicability*
</div>

<div class="column-center">

**Data**

Taiwan

College students, Acedamic staff

18 to 60

Current students to Phd

*NA*
</div>

<div class="column-right">

**Match**

Low

Medium

Medium

Medium

*Low to Medium*

</div>

#### $\color{brown}{\text{Association between Variables and Learning Outcome}}$

<div class="column-left">
**Variable**

Interest in learning (I)

Learning hours (T)

Teacher's instructional attitude (Mo)

I*Mo

T*Mo

</div>

<div class="column-center">
**Direction and Degree of Association**

Positive, Significant

Positive, Significant

Positive, Significant

Positive, Significantly strong

Positive, Significantly strong

</div>

<div class="column-right">
**Path Coefficient Value**

0.462

0.451

0.442

0.691

0.672

</div>

<span style="color:blue">When a teacher’s instructional attitude exerts a positive extraneous effect, H1, H2 and H3 appear relatively insignificant, compared with the increased significance of H4 and H5 statistically</span>.

>2. [THE EFFECT OF TEACHER COMMUNICATION ABILITY AND LEARNING MOTIVATION ON STUDENT LEARNING OUTCOMES IN ECONOMIC LESSONS FOR CLASS XI IPS SMA EKASAKTI IN PADANG ACADEMIC YEAR 2015/2016](https://click.endnote.com/viewer?doi=10.31933%2Fjige.v1i1.532&token=WzM4NzQwODksIjEwLjMxOTMzL2ppZ2UudjFpMS41MzIiXQ.YQ_qIxckhzLvpQEiikE2Iq_-xy4)


#### $\color{brown}{\text{Study Population}}$

<div class="column-left">
**Category**

Location

Population

Age

Education level

*Applicability*
</div>

<div class="column-center">
**Data**

Indonesia

High school student

16 to 17

Grade 11 

*NA*
</div>

<div class="column-right">
**Match**

Medium

Medium

Medium

Medium

*Medium*
</div>

#### $\color{brown}{\text{ Association between Variables and Learning Outcome }}$

<div class="column-left">
**Variable**

Teacher's communication skills (CS)

Student's motivation to learn (LM)

CS*LM

</div>

<div class="column-center">
**Direction and Degree of Association**

Positive, Significant

Positive, Significant

Positive, Significant

</div>

<div class="column-right">
**R-square Value**

NA

NA

0.216

</div>

#### $\color{brown}{\text{Changes in Value of Outcome}}$

Every  1  point  increase  in  communication  will  be  followed  by  an  increase  in learning  outcomes  of  0.155  and  every  1  point  increase  in  learning  motivation  will be followed by an increase in learning outcomes of 0.108.

Communication skills and learning motivation contribute  to  the  value  of  student  learning  outcomes  by  21.60%,  while  the  remaining 78.40% is contributed by other factors not examined in this study. Other variables  that  were  not  examined  were  internal  factors  (health,  intelligence,  interests)  and external factors (family and community environment).


> 3. [The  Correlation of  Motivation and  Habit with  Learning  Outcomes in New Normal Era](https://click.endnote.com/viewer?doi=10.25217%2Fji.v8i1.2749&token=WzM4NzQwODksIjEwLjI1MjE3L2ppLnY4aTEuMjc0OSJd.4RX3NsJrGDLYnH_KUh446TFrTj4)


#### $\color{brown}{\text{Study Population}}$

<div class="column-left">
**Category**

Location

Population

Age

Education level

*Applicability*
</div>

<div class="column-center">
**Data**

Indonesia

High school student

16 to 17

Grade 11 

*NA*
</div>

<div class="column-right">
**Match**

Medium

Medium

Medium

Medium

*Medium*
</div>

#### $\color{brown}{\text{ Association between Variables and Learning Outcome }}$

<div class="column-left">
**Variable**

Motivation (M) (self/external)

Habit (H)

M*H
</div>

<div class="column-center">
**Direction and Degree of Association**

Positive, Significant, Weak

Positive, Significant, Weak

Positive, Significant, Weak
</div>

<div class="column-right">
**R-square Value**

0.217

0.235

0.302
</div>

