---
title: "Priors_for_Learning_Outcome_Model"
author: "SM"
date: "2023-10-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

Forming Priors

Prior distributions for our model are set based on previous literature and inputs from experts. Experts' inputs are obtained via focused group discussion and survey. 

## Stage 1: Priors from literature

The objectives of collecting prior information from literature:

- To identify variables that have direct association with the targeted outcome
- To identify the direction and degree of associations between the variables and the outcome
- To explore the (qualitative) values of outcomes affected by different variables (when         applicable)

### Applicability and generalizability of data on our population 

The applicability and generalizability of data are determined by the extent of similarity between the study population and our population. 

#### Background info of our population

+ Location- Yangon, Myanmar
+ Population- Professional football players
+ Gender- Male and Female 
+ Age- 15 to 30
+ Education level- highschool to college level students, older players are university           graduates

#### Intervention 1: Improving Nutritional Self-reliance

+ Nutrition education (Nutrition Guide and a series of in-person classes)
    + Food groups (basic level)
    + Types of nutrients (basic level)
    + Healthy plate (basic level)
    + Macronutrient and fluid requirements (Intermediate to advance level)
    + Calculation of protein-energy requirements (Advance level)
    + Food exchange (Advance level)

#### Intervention 2: Guided Personalized Nutrition

+ Nutrition education (a 3-hour in-person class)
    + Food groups (basic level)
    + Types of nutrients (basic level)
    + Healthy plate (basic level)
    + Macronutrient and fluid requirements (Intermediate level)
    
### Collecting Priors from Literature Review

> 1. [The influences of interest in learning and learning hours on learning outcomes
of vocational college students in Taiwan: using a teacher’s instructional attitude
as the moderator](.http://wiete.com.au/journals/GJEE/Publish/vol13no3/01-Lee-Y-J.pdf)


```{r table1, tidy=FALSE, echo=FALSE}

data1 <- tribble(
  ~"Name",                  ~"Category",                          ~"Match",
  "Location",                "Taiwan",                              "Low",
  "Population",              "College students, lecturers",         "Medium",
  "Gender",                  "Male and Female",                     "High",
  "Age",                     "18 to 60",                            "Medium",
  "Education level",         "College studnets to Phd",             "Medium",
  "**Applicability**",       "**NA**",                              "**Low to Medium**"
)
knitr::kable((data1), booktabs = TRUE,
caption = 'Study Population')
```

<style>
.column-left{
  float: left;
  width: 33%;
  text-align: left;
}
.column-center{
  display: inline-block;
  width: 33%;
  text-align: center;
}
.column-right{
  float: right;
  width: 33%;
  text-align: right;
}
</style>

#### Association between Variables and Learning Outcome

<div class="column-left">
**Variable**

Interest in learning


</div>

<div class="column-center">
**Direction and Degree of Association**

Positive, Strong
</div>

<div class="column-right">
**Value of Outcome**

NA

</div>

  
